Evolution of Processes in Delivering Reliable Software within the European Scientific Arena

### 2019-02-13 paper-jgc.tex
Added text&reference of last year's EGI UMD publication.

The {\sl EGI--InSPIRE} (Integrated Sustainable Pan--European Infrastructure for
Researchers in Europe, May 2010 -- May 2014) project \cite{cordis:egi-inspire}
was the continuation of the {\sl EGEE--III} project, with the objective of establishing and
maintaining a sustainable European Grid Infrastructure, composed by a federation of National
Grid Initiatives and interoperable with other Grids worldwide.
This goal would be accomplished through the
development and maintenance of various operational tools -- such as the Operations Portal \cite{egi-ops},
the {\sl EGI} Helpdesk \cite{ggus}, or the Grid configuration database (GOCDB) \cite{gocdb} -- and the
management of the software provisioning process \cite{mario}, dealing with the validation and distribution of the software to
the production infrastructures. As a result, this process led to a production--ready
Grid computing middleware distribution named {\sl UMD} (Unified Middleware Distribution). At that time the {\sl UMD}
was a stack of about 250 software components from several technology providers, such
as {\sl EMI} and {\sl Globus}. In order to be distributed through UMD
repositories, the software had to be compliant with EGI's Quality Criteria (QC) \cite{egi-qc}. The
QC defined a set of requirements in different areas: documentation, deployment, security, information
model and operations.

@@

{\sl UMD} is still being used and
deployed in the European scientific e--Infrastructures under the follow--up
project {\sl EGI--Engage} (Engaging the EGI Community towards an Open Science
Commons) \cite{cordis:egi-engage}. This distribution is currently complemented
by a Cloud--specific one called {\sl CMD} (Cloud Middleware Distribution).

@@

>>>>

The {\sl EGI--InSPIRE} (Integrated Sustainable Pan--European Infrastructure for
Researchers in Europe, May 2010 -- May 2014) project \cite{cordis:egi-inspire}
was the continuation of the {\sl EGEE--III} project, with the objective of establishing and
maintaining a sustainable European Grid Infrastructure, composed by a federation of National
Grid Initiatives and interoperable with other Grids worldwide.
This goal would be accomplished through the
development and maintenance of various operational tools -- such as the Operations Portal \cite{egi-ops},
the {\sl EGI} Helpdesk \cite{ggus}, or the Grid configuration database (GOCDB) \cite{gocdb} -- and the
management of the software provisioning process (SWPP) \cite{mario}, dealing with the validation and distribution of the software to
the production infrastructures. As a result, this process led to a production--ready
Grid computing middleware distribution named {\sl UMD} (Unified Middleware Distribution). At that time the {\sl UMD}
was a stack of about 250 software components from several technology providers, such
as {\sl EMI} and {\sl Globus}. In order to be distributed through UMD
repositories, the software had to be compliant with EGI's Quality Criteria (QC) \cite{egi-qc}. The
QC defined a set of requirements in different areas: documentation, deployment, security, information
model and operations.

@@

{\sl UMD} is still being used and
deployed in the European scientific e--Infrastructures under the follow--up
project {\sl EGI--Engage} (Engaging the EGI Community towards an Open Science
Commons) \cite{cordis:egi-engage}. This distribution is currently complemented
by a Cloud--specific one called {\sl CMD} (Cloud Middleware Distribution). The
increase in the number of products that the new CMD distribution brought in,
compromised the effectiveness of the SWPP realization, in particular the
software validation phase. The modernization of the EGI QC validation was
accomplished through the adoption of automation, by means of the programmatic
evaluation of its fundamental quality requirements \cite{orviz2018umd}.

@@

\bibitem{orviz2018umd}
P. Orviz \emph{et al.},
``umd-verification: Automation of Software Validation for the EGI Federated e-Infrastructure,''
\emph{J. Grid Comp.},
vol. 16, no. 4, pp. 683--696, 2018.
